# Coursera Machine Learning Project

## loading packages and data

```{r loading, eval=F}
library(data.table)
library(caret)
library(ggplot2)
library(knitr)
library(xtable)
library(randomForest)
library(foreach)

raw.train  <- fread("pml-training.csv", na.strings=c("#DIV/0!", ""))
raw.test <- fread("pml-testing.csv", na.strings=c("#DIV/0!", ""))
```

### We removed excel error strings `#DIV/0!` and empty strings and replace these with `NA` values

## Cleaning data

```{r cleaning, eval=F}
na.cols <- raw.train[,sapply(.SD, function(x) any(is.na(x)))]
na.cols2 <- raw.test[,sapply(.SD, function(x) any(is.na(x)))]
```

### We removed any features that contained NA values.

```{r features, eval=F}
drop.unwanted.features <- function(x) {
    x[,!c("V1", "user_name", "raw_timestamp_part_1", "raw_timestamp_part_2", "cvtd_timestamp", "new_window", "num_window"),with=F]
}

columns_with_values <- drop.unwanted.features(raw.train[,eval(names(which(na.cols == F))),with=F])
```

### We are interested only in columns that have values

## Generating files:

```{r files, eval=F}
write.pml.predictions <- function(x) {
    n = length(x)
    for(i in 1:n){
        filename = paste0("problem_id_",i,".txt")
        write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
    }
}
```

## Cross Validation, Modeling, Prediction

```{r prediction, eval=F}
submit.prediction <- function(x, testset) {
    in.train <- createDataPartition(x$classe, p=.60, list=FALSE)
    train <- x[in.train[,1]]
    model.rf <- train(y=as.factor(train$classe), x=train[,!"classe",with=F], tuneGrid=data.frame(mtry=3), trControl=trainControl(method="none"))  
    write.pml.predictions(predict(model.rf, newdata=drop.unwanted.features(testset[,eval(names(which(na.cols2 == F))[-60]),with=F])))
    
}
```

Now to obtain 20 files we run the command:

submit.prediction(columns_with_values, raw.test)
